SMT-COMP 20243\\ 19th International Satisfiability Modulo Theory Competition

### 2024-07-19 2024/slides/presresults/input_for_certificates.tex
Updated slides with QF_BVFP incr. results.

\MakeOnePage{Algaroba}{}{\withtrack{QF\_Datatypes}{\seq,\paral,\fast}}{}{}{}

@@

\MakeOnePage{Bitwuzla}{}{\withtrack{Bitvec}{\sat}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_Bitvec}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_Equality\_Bitvec}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast}}{\withtrack{ABVFP}{\sat}, \withtrack{ABVFPLRA}{\sat}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFBV}{\fast}, \withtrack{UFBV}{\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat,\fast}}{s}{s}

@@

\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\fast}, \withtrack{QF\_FPLRA}{\fast}}{}{s}

@@

\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast}}{\withtrack{Arith}{\seq,\paral,\unsat}, \withtrack{Bitvec}{\seq,\paral,\unsat}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_LinearArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_MachineArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_NonLinearArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_Datatypes}{\sat}, \withtrack{QF\_Equality}{\sat}, \withtrack{QF\_Equality\_NonLinearArith}{\unsat}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat}}{\withtrack{FP}{\fast}, \withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat}, \withtrack{NRA}{\sat}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_AUFNIA}{\seq,\paral,\fast}, \withtrack{QF\_AX}{\fast}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_LIRA}{\fast}, \withtrack{QF\_UFBVDT}{\seq,\paral,\fast}, \withtrack{QF\_UFDT}{\seq,\paral}, \withtrack{QF\_UFDTNIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_UFFPDTNIRA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFLRA}{\unsat}}{s}{s}

@@

\MakeOnePage{iProver v3.9}{}{}{\withtrack{ALIA}{\paral,\unsat}, \withtrack{UF}{\fast}, \withtrack{UFDTNIA}{\paral,\unsat}, \withtrack{UFLRA}{\seq,\paral,\unsat,\fast}, \withtrack{UFNIRA}{\seq,\unsat}}{}{s}

@@

\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality\_LinearArith}{\unsat}, \withtrack{QF\_LinearIntArith}{\seq,\paral}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_AX}{\seq,\paral,\sat}, \withtrack{QF\_LIA}{\sat}, \withtrack{QF\_LRA}{\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat}}{s}{s}

@@

\MakeOnePage{OSTRICH}{}{}{\withtrack{QF\_SNIA}{\seq,\paral,\sat,\fast}}{}{}

@@

\MakeOnePage{SMT-RAT}{}{}{\withtrack{NRA}{\unsat,\fast}}{}{}

@@

\MakeOnePage{SMTInterpol}{}{\withtrack{QF\_Equality\_LinearArith}{\seq,\paral,\sat}}{\withtrack{ALIA}{\sat}, \withtrack{ANIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ANIA}{\unsat,\fast}, \withtrack{QF\_AUFLIA}{\fast}, \withtrack{QF\_AX}{\unsat}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_LIRA}{\sat}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UF}{\sat}, \withtrack{QF\_UFBVDT}{\sat,\unsat}, \withtrack{QF\_UFDTLIA}{\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\unsat,\fast}, \withtrack{QF\_UFLIA}{\unsat}, \withtrack{UFLIA}{\sat}}{}{s}

@@

\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\sat}}{}{}{}

@@

\MakeOnePage{Yices2}{}{\withtrack{QF\_Equality}{\fast}, \withtrack{QF\_Equality\_Bitvec}{\fast}, \withtrack{QF\_Equality\_LinearArith}{\fast}, \withtrack{QF\_Equality\_NonLinearArith}{\seq,\paral,\sat,\fast}, \withtrack{QF\_LinearIntArith}{\fast}, \withtrack{QF\_LinearRealArith}{\fast}, \withtrack{QF\_NonLinearIntArith}{\fast}, \withtrack{QF\_NonLinearRealArith}{\fast}}{\withtrack{QF\_LIRA}{\seq,\paral,\unsat}, \withtrack{QF\_RDL}{\seq,\paral,\sat}, \withtrack{QF\_UFLRA}{\seq,\paral}, \withtrack{QF\_UFNRA}{\unsat}}{s}{s}

@@

\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}, \withtrack{Bitvec}{\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}, \withtrack{NRA}{\seq,\paral}}{s}{s}
\MakeOnePage{Z3-alpha}{}{\withtrack{QF\_Datatypes}{\unsat}, \withtrack{QF\_Equality}{\seq,\paral,\unsat}, \withtrack{QF\_LinearIntArith}{\sat}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_AUFBV}{\unsat}, \withtrack{QF\_IDL}{\seq,\paral,\unsat}, \withtrack{QF\_NIRA}{\fast}, \withtrack{QF\_RDL}{\unsat}}{s}{s}

>>>>

\MakeOnePage{Algaroba}{}{\withtrack{QF\_Datatypes}{\seq,\paral,\fast}}{\withtrack{QF\_DT}{\sat}}{}{}

@@

\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat}, \withtrack{Equality\_MachineArith}{\inc,\uc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{QF\_ADT\_BitVec}{\mv}, \withtrack{QF\_Bitvec}{\seq,\paral,\unsat,\fast,\inc}, \withtrack{QF\_Equality\_Bitvec}{\seq,\paral,\sat,\unsat,\inc}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{ABVFP}{\sat}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{BVFPLRA}{\uc}, \withtrack{QF\_ABV}{\uc\textsuperscript\seq}, \withtrack{QF\_ABVFP}{\mv}, \withtrack{QF\_BVFPLRA}{\mv}, \withtrack{QF\_FPLRA}{\mv}, \withtrack{QF\_UFBV}{\fast}, \withtrack{UFBV}{\fast}}{s}{s}

@@

\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_ABVFPLRA}{\unsat}, \withtrack{QF\_FP}{\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}}{}{s}

@@

\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{Equality\_LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{Equality\_MachineArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality\_NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{FPArith}{\uc}, \withtrack{QF\_Datatypes}{\sat,\uc}, \withtrack{QF\_Equality\_LinearArith}{\uc\textsuperscript\paral}, \withtrack{QF\_Equality\_NonLinearArith}{\unsat,\inc,\uc\textsuperscript\seq,\mv}, \withtrack{QF\_FPArith}{\mv}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat}, \withtrack{QF\_Strings}{\uc}}{\withtrack{ANIA}{\uc}, \withtrack{AUFBV}{\uc\textsuperscript\paral}, \withtrack{AUFBVDTLIA}{\uc}, \withtrack{AUFBVDTNIRA}{\uc}, \withtrack{AUFDTLIRA}{\uc\textsuperscript\seq}, \withtrack{AUFFPDTNIRA}{\uc}, \withtrack{AUFLIRA}{\uc\textsuperscript\seq}, \withtrack{AUFNIA}{\uc\textsuperscript\paral}, \withtrack{BVFPLRA}{\unsat}, \withtrack{FP}{\fast}, \withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat}, \withtrack{QF\_AUFLIA}{\inc,\uc\textsuperscript\seq}, \withtrack{QF\_AX}{\mv}, \withtrack{QF\_BVFP}{\inc}, \withtrack{QF\_FP}{\sat,\uc}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_LIA}{\mv}, \withtrack{QF\_SNIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_UFBVDT}{\seq,\paral,\unsat,\fast,\uc,\mv}, \withtrack{QF\_UFDT}{\seq,\paral,\mv}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc\textsuperscript\seq,\mv}, \withtrack{QF\_UFDTNIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_UFFPDTNIRA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFLRA}{\inc,\uc\textsuperscript\seq}, \withtrack{UFDT}{\uc\textsuperscript\seq}, \withtrack{UFDTLIA}{\uc\textsuperscript\seq}, \withtrack{UFDTNIA}{\uc\textsuperscript\seq}, \withtrack{UFFPDTNIRA}{\uc}, \withtrack{UFIDL}{\uc\textsuperscript\seq}, \withtrack{UFLRA}{\uc}, \withtrack{UFNIRA}{\uc\textsuperscript\seq}}{s}{s}

@@

\MakeOnePage{iProver v3.9}{}{}{\withtrack{ALIA}{\paral,\unsat}, \withtrack{UF}{\fast}, \withtrack{UFNIRA}{\seq,\unsat}}{}{s}

@@

\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality}{\mv}, \withtrack{QF\_Equality\_LinearArith}{\unsat,\mv}, \withtrack{QF\_LinearIntArith}{\seq,\paral,\mv}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\sat}, \withtrack{QF\_LRA}{\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat}}{s}{s}

@@

\MakeOnePage{SMT-RAT}{}{\withtrack{QF\_NonLinearRealArith}{\mv}}{\withtrack{NRA}{\seq,\paral,\unsat,\fast}}{}{}

@@

\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\uc,\mv}}{\withtrack{Arith}{\uc}, \withtrack{Equality}{\uc\textsuperscript\paral}, \withtrack{Equality\_LinearArith}{\uc}, \withtrack{Equality\_NonLinearArith}{\uc}, \withtrack{QF\_ADT\_LinArith}{\mv}, \withtrack{QF\_Datatypes}{\mv}, \withtrack{QF\_Equality\_LinearArith}{\seq,\paral,\sat,\inc,\uc\textsuperscript\seq}, \withtrack{QF\_Equality\_NonLinearArith}{\uc\textsuperscript\paral}, \withtrack{QF\_NonLinearIntArith}{\inc,\uc}, \withtrack{QF\_NonLinearRealArith}{\uc}}{\withtrack{ALIA}{\sat}, \withtrack{ANIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ALIA}{\uc\textsuperscript\paral}, \withtrack{QF\_ANIA}{\unsat,\fast,\inc,\uc\textsuperscript\seq,\mv}, \withtrack{QF\_AUFNIA}{\sat,\uc\textsuperscript\seq,\mv}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_LIRA}{\uc\textsuperscript\paral}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFBVDT}{\sat}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc\textsuperscript\paral}, \withtrack{QF\_UFDTNIA}{\uc\textsuperscript\seq,\mv}, \withtrack{QF\_UFLIA}{\unsat,\mv}, \withtrack{QF\_UFNRA}{\uc\textsuperscript\seq}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}{s}{s}

@@

\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\sat,\mv}}{}{}{}

@@

\MakeOnePage{Yices2}{\withtrack{Largest Contribution}{\uc,\mv}}{\withtrack{Equality}{\uc\textsuperscript\seq}, \withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Equality\_Bitvec}{\fast,\uc,\mv}, \withtrack{QF\_Equality\_Bitvec\_Arith}{\inc}, \withtrack{QF\_Equality\_LinearArith}{\fast}, \withtrack{QF\_Equality\_NonLinearArith}{\seq,\paral,\sat,\fast}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\fast,\uc}, \withtrack{QF\_NonLinearIntArith}{\fast,\mv}, \withtrack{QF\_NonLinearRealArith}{\fast}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_AUFNIA}{\unsat}, \withtrack{QF\_IDL}{\mv}, \withtrack{QF\_LIRA}{\sat,\mv}, \withtrack{QF\_RDL}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_UFLIA}{\inc,\uc\textsuperscript\seq}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_UFNRA}{\unsat,\mv}, \withtrack{UF}{\uc\textsuperscript\paral}}{s}{s}

@@

\MakeOnePage{YicesQS}{}{\withtrack{Arith}{\sat,\fast}, \withtrack{Bitvec}{\fast}}{\withtrack{LRA}{\seq,\paral,\unsat}}{s}{}

@@

\MakeOnePage{Z3-alpha}{}{\withtrack{QF\_Datatypes}{\unsat}, \withtrack{QF\_LinearIntArith}{\sat}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_AUFBV}{\unsat}, \withtrack{QF\_IDL}{\seq,\paral,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\unsat}, \withtrack{QF\_NIRA}{\fast}}{s}{s}

### 2024-07-19 2024/slides/presresults/slides.tex
Updated slides with QF_BVFP incr. results.

@@

\begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
\item Algaroba
\vitem COLIBRI
\vitem iProver
\vitem OpenSMT
\vitem plat-smt
\vitem SMTS
\vitem STP
\vitem (STP-Parti-Bitwuzla)
\vitem Z3-Noodler
    \end{itemize}
  \end{frame}

@@

  \vitem We manually resolved the disagreements: authors confirmed solver
  unsoundness
  \vitem We had 4 solvers with soundness issues:
    \begin{itemize}
      \item Amaya (\& Fixed)
      \item cvc5 (\& Fixed)
      \item iProver (\& Fixed)
      \item OSTRICH (\& Fixed)
    \end{itemize}
  \end{itemize}
  \end{frame}

@@

\begin{frame}{SMT-COMP organizing committee}
  Three people organize the SMT-COMP.  In 2024:
  \begin{itemize}
  \item Fran\c{c}ois Bobot
  \item Martin Bromberger
  \item Martin Jon\'{a}\v{s}
  \end{itemize}

@@

\begin{frame}{Acknowledgements}
  \begin{itemize}
    \item \emph{Andrea Micheli}: pysmt
    \item \emph{Guillaume Bury, FB.}: Model Validator
    \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
    \item \emph{Robert Jones, Benjamin F Jones, and team}: Cloud/Parallel Track
    \item \emph{Dirk Beyer and Philipp}: BenchExec and VerifierCloud support   
    \item \emph{Aaron Stump}: StarExec support
  \end{itemize}
  \bigskip

@@

  \small
  \begin{itemize}
    \item TODO
  \end{itemize}
\end{frame}

>>>>

\myvideopdf{Algaroba}{Algaroba.mp4}

@@

\begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
\item COLIBRI
\item iProver
\item OpenSMT
\item plat-smt
\item SMTS
\item STP
\item (STP-Parti-Bitwuzla)
\item Z3-Noodler
    \end{itemize}
  \end{frame}

@@

  \vitem We manually resolved the disagreements: authors confirmed solver
  unsoundness
  \vitem We had 4 solvers with soundness issues:
    \begin{itemize}
      \item Amaya (fixed version available)
      \item cvc5 (fixed version available)
      \item iProver (fixed version available)
      \item OSTRICH (fixed version available)
    \end{itemize}
  \end{itemize}
  \end{frame}

@@

\begin{frame}{SMT-COMP organizing committee}
  Three people organize the SMT-COMP.  In 2024:
  \begin{itemize}
  \item Fran\c{c}ois Bobot
  \item Martin Bromberger
  \item Martin Jon\'{a}\v{s}
  \end{itemize}
  \bigskip

@@

\begin{frame}{Acknowledgements}
  \begin{itemize}
    \item \emph{Andrea Micheli}: pysmt
    \item \emph{Guillaume Bury, FB.}: Model Validator
    \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
    \item \emph{Robert Jones, Benjamin F Jones, and team}: Cloud/Parallel Track
    \item \emph{Dirk Beyer and Philipp Wendler}: BenchExec and VerifierCloud support   
    \item \emph{Aaron Stump}: StarExec support
  \end{itemize}
  \bigskip

@@

  \small
  \begin{itemize}
    \item Matthias Heizmann (30)
    \item Mirek Olšák, Mikoláš Janota, Chad E. Brown (266)
    \item Tomas Kolarik (1046)
    \item Martin von Berg, Arthur Sanin, Aron Spang, Christoph Beierle (80)
    \item Michele Chiari, Francesco Pontiggia (14)
    \item Tobias Winkler (6)
    \item Certora (submitted by Antti Hyvärinen) (210)
    \item Denghang Hu, Rongcheng Li, Zhilin Wu, Philipp Rummer, Oliver Markgraf (3287)
    \item Federico Mora (500)
    \item Oliver Markgraf (17)
    \item Shilpi Goel, Nathan Wetzler, Yan Peng, Jim Grundy (Courtesy of AWS) (9)
  \end{itemize}
\end{frame}
